---
title: "Stats 100: Final Project"
author: "Faris Bdair"
date: "03/14/2024"
header-includes:
   - \usepackage{bbm, amsmath,amsfonts,amsthm,amssymb,mathrsfs,amsxtra,amscd,latexsym, xcolor, graphicx, fvextra}
   - \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
output: pdf_document
---
# Predicting Fifa World Cup

# Acknowledgements

```{r}
## Load in necessary libraries
suppressPackageStartupMessages(library(knitr)) #makes pdfs
suppressPackageStartupMessages(library(latex2exp))
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(nnet))
suppressPackageStartupMessages(library(lmtest))
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
## Load in files from source

# All international soccer games ever
games = read.csv('Fifa_Results_All.csv')

# A list of fifa rankings since 12-31-1992
rankings = read.csv('FIFA_Rankings.csv')

# A dataset of the 2022 world cup with teams, groups, confederations, ELOs and results
Test_WC_2022_dataset = read.csv('2022_World_Cup.csv')

# Create a dataset of only World Cup and World Cup Qualifiers
WC_all_time = filter(games,
                     tournament == 'FIFA World Cup qualification'  |
                       tournament == 'FIFA World Cup')

# Create a dataset of only games between 2003 and 2022 (2006 Qualifiers -> 2022 Qualifiers)
WC_dataset = filter(WC_all_time, date >= 2003 & date <= 2022)
```


```{r}
## Creates a new dataframe with all the data we want in the same place

# Since our rankings dataframe has repeats, we need to select the most common confederation associated with a country and assign that confederation to the country
country_confederation = rankings %>%
  group_by(country_full, confederation) %>%
  summarise(count = n(), .groups = 'drop') %>%
  arrange(desc(count)) %>%
  group_by(country_full) %>%
  slice(1) %>%
  ungroup() %>%
  select(-count)

# This creates a dataframe sorted by country again removing repeats and separating ranking dates into seperate columns
Elo_rankings = rankings %>%
  select(country_full, rank_date, total_points) %>%
  pivot_wider(names_from = rank_date, values_from = total_points)

# Merge the two data frames to get with with team, confederation, and all its rankings ever
Country_Data <-
  left_join(country_confederation, Elo_rankings, by = "country_full")
```

```{r}
## Using our new Country_Data dataframe to add confederations to our WC_dataset

# Adding home_confederation and away_confederation columns to our dataset
WC_dataset$home_confederation = NA
WC_dataset$away_confederation = NA

# Update home_confederation based on Country_Data
WC_dataset <- WC_dataset %>%
  left_join(
    Country_Data %>% select(country_full, confederation),
    by = c("home_team" = "country_full")
  ) %>%
  mutate(home_confederation = coalesce(confederation, home_confederation)) %>%
  select(-confederation)

# Update away_confederation based on Country_Data
WC_dataset <- WC_dataset %>%
  left_join(
    Country_Data %>% select(country_full, confederation),
    by = c("away_team" = "country_full")
  ) %>%
  mutate(away_confederation = coalesce(confederation, away_confederation)) %>%
  select(-confederation)
```

```{r}
## Use Country_Data to find the date of the most recent rankings for a team before the game in question

# Convert the date column names (excluding country_full and confederation) in Country_Data to Date objects
date_columns <- names(Country_Data)[-c(1, 2)]
date_columns_dates <-
  as.Date(date_columns, format = "%Y-%m-%d") # Adjust format as necessary

# Function to find the latest ranking date column name before a given date
find_latest_date_column_before <- function(game_date) {
  game_date <- as.Date(game_date)
  valid_dates <-
    date_columns_dates[which(date_columns_dates < game_date)]
  if (length(valid_dates) == 0)
    return(NA) # Return NA if no earlier date is found
  latest_date <- max(valid_dates)
  column_name <-
    date_columns[which(date_columns_dates == latest_date)]
  return(column_name)
}

# Apply this function for each row in WC_dataset to find the relevant ranking dates
WC_dataset <- WC_dataset %>%
  mutate(latest_ranking_date = map_chr(date, find_latest_date_column_before))
```

```{r}
## Function to find the most recent ELO for a team on a given date
find_ELO_for_team_and_date <- function(team, date_column) {
  # Filter Country_Data for the given team
  team_data = filter(Country_Data, country_full == team)
  # Extract the ELO value from the column corresponding to the latest_date_column
  elo_value = team_data[[date_column]]
  
  return(elo_value)
}
```

```{r}
## Creating home_ELO and away_ELO columns in WC_dataset
WC_dataset <- WC_dataset %>%
  rowwise() %>%
  mutate(
    # Adding home_ELO
    home_ELO = find_ELO_for_team_and_date(home_team, latest_ranking_date),
    # Adding away_ELO
    away_ELO = find_ELO_for_team_and_date(away_team, latest_ranking_date)
  ) %>%
  ungroup()
```

```{r}
# Remove games where either home or away ELO is null indicating there is no ranking for the team at the time played
WC_dataset = filter(WC_dataset, home_ELO != 'NULL' &
                      away_ELO != 'NULL')
```

```{r} 
## Used to help clean data
# Filter rows where home_confederation or away_confederation is NA
null_confederation_games = filter(WC_dataset,
                                  is.na(home_confederation) | is.na(away_confederation))

# Filter rows where either home_ELO or away_ELO is NA
games_with_null_ELO = filter(WC_dataset, home_ELO == 'NULL' |
                               away_ELO == 'NULL')

# If there exists a game with null ELO or null confederation ...
if (nrow(games_with_null_ELO) > 0 ||
    nrow(null_confederation_games) > 0) {
  # Print the games with null_confederation
  print(null_confederation_games)
  # Print the games with null_ELO
  print(games_with_null_ELO)
}
```

```{r}
## Creates comparison metrics to use in regression as well as an outcome metric and adds as columns to WC_dataset
WC_dataset <- WC_dataset %>%
  rowwise() %>%
  mutate(
    # Finds the difference in ELO between the two teams
    ELO_difference = home_ELO - away_ELO,
    # Finds the ratio of the ELO between the two teams
    ELO_ratio = home_ELO / away_ELO,
    # Goal Differential from home team's perspective
    home_GD = home_score - away_score,
    # Outcome from home team's perspective, 1 for win, 0 for draw, -1 for loss
    home_result = ifelse(home_score > away_score, 1,
                         ifelse(away_score > home_score,-1, 0))
  ) %>%
  ungroup()
```

```{r}
## Create six different models to compare using difference vs ratio as well as including confederations or not
# Compares with ELO_difference, excludes confederation
dif_model = multinom(home_result ~ ELO_difference, data = WC_dataset)

# Compares with ELO_ratio, excludes confederation
rat_model = multinom(home_result ~ ELO_ratio, data = WC_dataset)

# Compares with ELO_difference and ELO_ratio, excludes confederation
dif_rat_model = multinom(home_result ~ ELO_difference + ELO_ratio, data = WC_dataset)

# Compares with ELO_difference, includes confederation
confed_dif_model = multinom(home_result ~ ELO_difference + home_confederation + away_confederation,
                            data = WC_dataset)

# Compares with ELO_ratio, includes confederation
confed_rat_model = multinom(home_result ~ ELO_ratio + home_confederation + away_confederation,
                            data = WC_dataset)

# Compares with ELO_difference and ELO_ratio, includes confederation
confed_dif_rat_model = multinom(
  home_result ~ ELO_difference + ELO_ratio + home_confederation + away_confederation,
  data = WC_dataset
)

```

```{r}

## Takes in all the deviances and plots them
# Load necessary library
library(ggplot2)

# Takes in all the deviances and adds them to a list
Residual_Deviance <- c(
  deviance(dif_model),
  deviance(rat_model),
  deviance(dif_rat_model),
  deviance(confed_dif_model),
  deviance(confed_rat_model),
  deviance(confed_dif_rat_model)
)
# Names the models
Model <- c('ELO_D',
           'ELO_R',
           'ELO_DR',
           'C_ELO_D',
           'C_ELO_R',
           'C_ELO_DR')

# Create a data frame from the vectors
data <- data.frame(Model, Residual_Deviance)

# Adjust Model factor levels to reflect the order of Residual_Deviance
data$Model <- factor(data$Model, levels = data$Model[order(data$Residual_Deviance)])

# Plot the Residual Deviance by model using the sorted data
ggplot(data, aes(x = reorder(Model, Residual_Deviance), y = Residual_Deviance, fill = Model)) +
  geom_bar(stat = "identity") +
  coord_flip() + # Flipping the coordinates to have horizontal bars
  labs(title = "Residual Deviance by Model",
       x = "Model",
       y = "Residual Deviance") +
  theme_minimal() +
  scale_fill_brewer(palette = "Spectral") +
  coord_cartesian(ylim = c(6000, 8000)) # Optional: Adjust based on your specific data range
```

```{r}
## Runs three likelihood ratio tests to see if including confederation is a stastically significant inclusion
# LRT test for models using ELO_difference
lrt_dif_result = lrtest(dif_model, confed_dif_model)
# LRT test for models using ELO_ratio
lrt_rat_result = lrtest(rat_model, confed_rat_model)
# LRT test for models using both ELO_difference and ELO_ratio
lrt_dif_rat_result = lrtest(dif_rat_model, confed_dif_rat_model)

# Prints results
print(lrt_dif_result)
print(lrt_rat_result)
print(lrt_dif_rat_result)
```
# As we can see from the lower standard errors, residual deviance, and AIC, the difference model seems to be more effective at predicting outcomes. Additionally, as shown by the statistically significant LRTs, including the confederation seems to make the predictions more accuracte meaning our confed_dif_model is the best predictor. This is interesting to note and we will continue to try and prove this later.

# Now we need to test our 6 models
# To do this we must first use the models to calculate the probabilities of a win, draw, or loss
# We must then use these probabilities to predict single games
# We must then use the single games to predict the group stage
# We must then use the group stage to generate a bracket
# We must then compare our generated bracket to the actual bracket
# We must then repeat 10000 times
```{r}
## Create a function that generates the probabilities of a Win, Draw, and Loss using our model and its inputs
W_D_L_probabilities <-
  function(model,
           ELO_difference,
           ELO_ratio,
           home_confederation,
           away_confederation) {
    # Start by creating a data frame with the ELO_difference and ELO_ratio
    match_data <-
      data.frame(ELO_difference = ELO_difference, ELO_ratio = ELO_ratio)
    # Conditionally add confederation data if it's not NULL
    if (!is.null(home_confederation) &&
        !is.null(away_confederation))  {
      match_data$home_confederation <- home_confederation
      match_data$away_confederation <- away_confederation
    }
    # Use the model to generate probabilities
    predictions <- predict(model, match_data, type = "probs")
    return(predictions)
  }
```

```{r}
## Create a function that uses W_D_L probabilities to give a definitive outcome using our model and its inputs
simulate_single_game <-
  function(model,
           ELO_difference,
           ELO_ratio,
           home_confederation,
           away_confederation) {
    # Get probabilities for Win, Draw, and Loss
    probabilities <-
      W_D_L_probabilities(model,
                          ELO_difference,
                          ELO_ratio,
                          home_confederation,
                          away_confederation)
    
    # Randomly generate a number between 0 and 1
    random_number <- runif(1)
    
    # Define the cumulative probabilities for selecting the outcome
    cumulative_prob <- cumsum(probabilities)
    
    # Determine the outcome based on the random number and cumulative probabilities
    if (random_number <= cumulative_prob["-1"]) {
      # Home loss
      outcome <- -1
    } else if (random_number <= cumulative_prob["0"]) {
      # Home draw
      outcome <- 0
    } else {
      # Home win
      outcome <- 1
    }
    
    return(outcome)
  }
```

```{r}
## Create a function that takes in our WC Group Stage, predicts every single game, and returns each team's rank in their group
simulate_group_stage <- function(model, teams) {
  # Initialize a vector to keep track of points for each team
  teams$Points <- 0
  
  # Split the dataframe by group
  groups <- split(teams, teams$Group)
  
  # Iterate through each group
  for (group_name in names(groups)) {
    group <- groups[[group_name]]
    
    # Simulate each team playing every other team once within the group
    for (i in 1:(nrow(group) - 1)) {
      for (j in (i + 1):nrow(group)) {
        # Use predict_single_game to get the outcome of the game and save it in home_result
        home_result <-
          simulate_single_game(
            model,
            ELO_difference = group$ELO[i] - group$ELO[j],
            ELO_ratio = group$ELO[i] / group$ELO[j],
            home_confederation = group$Confederation[i],
            away_confederation = group$Confederation[j]
          )
        # Update points based on match outcome
        if (home_result == 1) {
          # Home win
          group$Points[i] <- group$Points[i] + 3
        } else if (home_result == 0) {
          # Home draw
          group$Points[i] <- group$Points[i] + 1
          group$Points[j] <- group$Points[j] + 1
        } else {
          # Home loss
          group$Points[j] <- group$Points[j] + 3
        }
      }
    }
    # Update the points in the main dataframe
    teams$Points[teams$Group == group_name] <- group$Points
  }
  
  # Rank teams within their groups, break ties randomly
  teams$rank <-
    ave(
      teams$Points,
      teams$Group,
      FUN = function(x)
        rank(-x, ties.method = "random")
    )
  
  return(teams)
}
```

```{r}
## Create a function that takes in the results of our simulated group stage and returns a bracket in 1A2B, 1C2D, ... format
create_bracket <- function(Group_Stage) {
  # Filter the eight group winners
  winners = filter(Group_Stage, rank == "1")
  # Filter the eight group runners up
  runners_up = filter(Group_Stage, rank == "2")
  # Define the specific order of matchups as per the World Cup regulations
  matchups_order <-
    c("1A2B", "1C2D", "1E2F", "1G2H", "1B2A", "1D2C", "1F2E", "1H2G")
  
  # Initialize an empty dataframe to store the matchups
  matchups <-
    data.frame(Team1 = character(),
               Team2 = character(),
               stringsAsFactors = FALSE)
  
  # Loop through the matchups_order to create matchups
  for (matchup in matchups_order) {
    # Extract the groups for the winner and runner-up in the matchup
    group_winner <- substr(matchup, 2, 2)
    group_runner_up <- substr(matchup, 4, 4)
    
    # Find the corresponding teams
    winner <- winners[winners$Group == group_winner, , drop = FALSE]
    runner_up <-
      runners_up[runners_up$Group == group_runner_up, , drop = FALSE]
    
    # Append to the matchups dataframe, retaining additional information
    matchup_info <- data.frame(
      Team1 = winner$Team,
      Team2 = runner_up$Team,
      Team1_ELO = winner$ELO,
      Team2_ELO = runner_up$ELO,
      Team1_Confederation = winner$Confederation,
      Team2_Confederation = runner_up$Confederation,
      stringsAsFactors = FALSE
    )
    
    matchups <- rbind(matchups, matchup_info)
  }
  # matchups now contains the desired matchups along with additional info
  return(matchups)
}
```

```{r}
## Create a function that uses W_D_L probabilities to give a definitive outcome without draws using our model and its inputs
simulate_single_game_knockout <- function(model, matchup) {
  # Get probabilities for Win, Draw, and Loss
  probabilities <-
    W_D_L_probabilities(
      model,
      matchup$Team1_ELO - matchup$Team2_ELO,
      matchup$Team1_ELO / matchup$Team2_ELO,
      matchup$Team1_Confederation,
      matchup$Team2_Confederation
    )
  # Randomly generate a number between 0 and 1
  random_number <- runif(1)
  
  # Define the cumulative probabilities for selecting the outcome
  cumulative_prob <- cumsum(probabilities)
  # Determine the outcome based on the random number and cumulative probabilities
  if (random_number <= cumulative_prob["-1"]) {
    # Home loss
    outcome <- 2
  } else if (random_number > cumulative_prob["0"]) {
    # Home win
    outcome <- 1
  } else {
    # Extra Time
    
    # Randomly generate another number between 0 and 1 for ET
    ET_random_number <- runif(1)
    if (ET_random_number <= cumulative_prob["-1"]) {
      # Home loss
      outcome <- 2
    } else if (ET_random_number > cumulative_prob["0"]) {
      # Home win
      outcome <- 1
    } else {
      # Penalties 
      
      # Randomly selects a winner in penalties
      outcome <- sample(c(1,2), size = 1)
    }
  }
  return(outcome)
}
```

```{r}
## Create a function to simulate the outcome of an inputted bracket using our model and returning champion, runner up, and total teams correctly predicted
simulate_bracket <- function(model, bracket) {
  # Initializes our total_correct tracker
  Overall_correct = 0
  # This simulates a bracket
  current_round <- bracket
  # Initializes a variable for the round we are in correlated to the column # of that round in our dataset
  round = 5
  next_round <-
    data.frame(Team1 = character(),
               Team2 = character(),
               stringsAsFactors = FALSE)
  # As long as the current_round is not the final
  while (round < 8) {
    # Clear the next round
    next_round <- next_round[0, ]
    # Seperates every two matchups together
    for (i in seq(1, nrow(current_round), by = 2)) {
      team_1 = as.character(current_round[i, 1])
      team_2 = as.character(current_round[i, 2])
      team_3 = as.character(current_round[i + 1, 1])
      team_4 = as.character(current_round[i + 1, 2])
      # Puts the 4 teams that could play each other in the next round in one list
      teams = c(team_1, team_2, team_3, team_4)
      for (team in teams) {
        # Adds 1 to overall correct if these teams made the current_round of the tournament
        if (Test_WC_2022_dataset[Test_WC_2022_dataset$Team == team, round] == 1) {
          Overall_correct = Overall_correct + 1
        }
      }
      # Simulate these two matches to get the winners for the next round
      team_name = as.character(current_round[i, 1])
      game1 <-
        simulate_single_game_knockout(model,
                                      current_round[i, , drop = FALSE])
      game2 <- simulate_single_game_knockout(model,
                                             current_round[i + 1, , drop = FALSE])
      # Prepare the matchup for the next round
      next_round <-
        rbind(
          next_round,
          data.frame(
            Team1 = current_round[i, game1],
            Team2 = current_round[i + 1, game2],
            Team1_ELO = current_round[i, game1 + 2],
            Team2_ELO = current_round[i + 1, game2 + 2],
            Team1_Confederation = current_round[i, game1 + 4],
            Team2_Confederation = current_round[i + 1, game2 + 4]
          )
        )
    }
    # Prepare the next round
    current_round <- next_round
    round = round + 1
  }
  # The final match to determine the champion
  Winner_Final <-
    simulate_single_game_knockout(model, current_round)
  # Figures out who was champion
  champion <-
    ifelse(Winner_Final == 1, current_round$Team1, current_round$Team2)
  # Figures out who was runner up
  runner_up <-
    ifelse(Winner_Final == 1, current_round$Team2, current_round$Team1)
  # Adds champion and runner_up to total correct count if correct
  if (Test_WC_2022_dataset[Test_WC_2022_dataset$Team == champion, 8] == 1) {
    Overall_correct = Overall_correct + 1
  }
  if (Test_WC_2022_dataset[Test_WC_2022_dataset$Team == runner_up, 8] == 1) {
    Overall_correct = Overall_correct + 1
  }
  if (Test_WC_2022_dataset[Test_WC_2022_dataset$Team == champion, 9] == 1) {
    Overall_correct = Overall_correct + 1
  }
  
  #returns champion, runner up, and overall correct in a list
  return(list(champion, runner_up, Overall_correct))
}
```

```{r}
## Create a function to simulate a World Cup from start to end
simulate_world_cup <- function(model, teams) {
  # Simulates group stage
  group_stage = simulate_group_stage(model, teams)
  # Converts group stage into bracket
  bracket = create_bracket(group_stage)
  # Simulates the bracket
  results = simulate_bracket(model, bracket)
  return(results)
}
```

```{r}
## Create a function to simulate the World Cup 1000 times using a list of teams for the group stage
simulate_1000_world_cups <- function(model, teams) {
  # Initializes a variable with the total times the correct champion is picked across the 1000 simulations
  Correct_champion = 0
  # Initializes a variable with the total times the correct final matchup is picked across the 1000 simulations
  Correct_final = 0
  # Initializes a variable with the total times a winner is correctly picked across the 1000 simulations
  Overall_correct = 0
  # Number of simulations
  nsimulations = 1000
  # Initializes a variable with the number of games picked right by the best bracket picked across the 1000 simulations
  Max_correct = 0
  for (i in 1:nsimulations) {
    # Simulate 1 world cup
    results = simulate_world_cup(model, teams)
    if (results[1] == "Argentina") {
      # Increases correct_champion by 1 if Argentina was the simulated champion
      Correct_champion = Correct_champion + 1
    }
    if ((results[1] == "Argentina" && results[2] == "France") ||
        (results[1] == "France" && results[2] == "Argentina")) {
      # Increases correct_final by 1 if Argentina-France was the simulated final
      Correct_final = Correct_final + 1
    }
    # Increases overall_correct by the total number of games predicted in this simulation
    Overall_correct = Overall_correct + as.numeric(results[3])
    if (as.numeric(results[3]) > Max_correct) {
      # Resets Max_correct if this was the best_bracket so far
      Max_correct = as.numeric(results[3])
    }
  }
  # Calculates the average games correctly predicted across all 1000 simulations
  Average_correct = Overall_correct / nsimulations
  return(list(
    Correct_champion,
    Correct_final,
    Average_correct,
    Max_correct
  ))
}
```

```{r}
## Runs 1000 simulations for each of the 6 models
dif_accuracy = simulate_1000_world_cups(dif_model, Test_WC_2022_dataset)
rat_accuracy = simulate_1000_world_cups(rat_model, Test_WC_2022_dataset)
dif_rat_accuracy = simulate_1000_world_cups(dif_rat_model, Test_WC_2022_dataset)
confed_dif_accuracy = simulate_1000_world_cups(confed_dif_model, Test_WC_2022_dataset)
confed_rat_accuracy = simulate_1000_world_cups(confed_rat_model, Test_WC_2022_dataset)
confed_dif_rat_accuracy = simulate_1000_world_cups(confed_dif_rat_model, Test_WC_2022_dataset)
```


```{r}
## Put results into a dataframe
results <- data.frame(
  Model = c('ELO_D',
            'ELO_R',
            'ELO_DR',
            'C_ELO_D',
            'C_ELO_R',
            'C_ELO_DR'),
  Correct_Champion = c(
    dif_accuracy[[1]],
    rat_accuracy[[1]],
    dif_rat_accuracy[[1]],
    confed_dif_accuracy[[1]],
    confed_rat_accuracy[[1]],
    confed_dif_rat_accuracy[[1]]
  ),
  Correct_Finalists = c(
    dif_accuracy[[2]],
    rat_accuracy[[2]],
    dif_rat_accuracy[[2]],
    confed_dif_accuracy[[2]],
    confed_rat_accuracy[[2]],
    confed_dif_rat_accuracy[[2]]
  ),
  Average_Correct = c(
    dif_accuracy[[3]],
    rat_accuracy[[3]],
    dif_rat_accuracy[[3]],
    confed_dif_accuracy[[3]],
    confed_rat_accuracy[[3]],
    confed_dif_rat_accuracy[[3]]
  ),
  Max_Correct = c(
    dif_accuracy[[4]],
    rat_accuracy[[4]],
    dif_rat_accuracy[[4]],
    confed_dif_accuracy[[4]],
    confed_rat_accuracy[[4]],
    confed_dif_rat_accuracy[[4]]
  )
)
```

```{r}
## Run various plots for statistical analysis

# Plot Correct_Champion results
ggplot(results, aes(x = Model, y = Correct_Champion, fill = Model)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Correct Champion Predictions by Model",
       y = "Number of Correct Predictions",
       x = "Model")

# Plot Correct_Finalists results
ggplot(results, aes(x = Model, y = Correct_Finalists, fill = Model)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Correct Final Predictions by Model",
       y = "Number of Correct Predictions",
       x = "Model")

# Plot Average_Correct results
ggplot(results, aes(x = Model, y = Average_Correct, fill = Model)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Average Correct Predictions by Model",
       y = "Average Correct Predictions Per Tournqment by Model (out of 31)",
       x = "Model") + coord_cartesian(ylim = c(12, 15))

# Plot Correct_Champion results
ggplot(results, aes(x = Model, y = Max_Correct, fill = Model)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Number of Predictions Correct in the Most Accurate Bracket by Model",
       y = "Number of Correct Predictions",
       x = "Model")


# Sort Source Data by tournament only including those with over 250 games played
tournament_counts <- games %>%
  group_by(tournament) %>%
  summarise(count = n()) %>%
  filter(count > 250) # Keep only those tournaments with more than 100 occurrences
# Plot the data
ggplot(tournament_counts, aes(x = reorder(tournament, count), y = count)) +
  geom_bar(stat = "identity") + # Use geom_col() as an alternative
  theme_minimal() +
  labs(title = "Tournament Appearance Counts",
       x = "Tournament",
       y = "Count (min 250)") +
  coord_flip()
```